\chapter{Scenarios}
	In this chapter you will find the most important scenarios among the entire set of possible scenarios that a user could face in interacting with the final application.\\
	I decided to list only the most important, because it happens very often to list scenarios which are self explanatory and so they are only a waste of time to read and to write.

	I think that the scenarios that needs some clarification are:
	\newcommand{\scenarioLogin}{The Log In}
	\newcommand{\scenarioRooms}{The Rooms}
	\newcommand{\scenarioBattle}{The Battle}
	\newcommand{\scenarioFellowship}{The Fellowship}
	\begin{itemize}
		\item \scenarioLogin 
		\item \scenarioRooms 
		\item \scenarioBattle 
		\item \scenarioFellowship
	\end{itemize}

	The subject of our scenarios will be John who heard about \SocialBattle{} by a great friend of him, Jill.\\
	This friend told him that the social network is highly addictive, so John decides to give it a try and sign up.

	\section{\scenarioLogin}
		John enters the home page of \SocialBattle{} and discovers that he can decide between three options:
		sign up with \Facebook, with \Twitter or without using any social network.
		John decides to sign up without any of the specified social networks, so he enters a nickname; his e-mail address and types his new password (he also retypes it for security reasons).\\
		Now John has subscribed to \SocialBattle{} and he can use it.\\
		First of all, John enters his profile and decides to edit it because he wants to add a new avatar. So he enters a new avatar and, watching at the ``edit profile'' page, he discovers that ha can bind his account to \Facebook{} and to \Twitter{} if he wants, even if he didn't do so in the sign up phase. John does it, so he performs the login with the two social networks.\\
		\SocialBattle{} informs John that, doing so, he will be able to share his results with his \Facebook{} and \Twitter{} friends.

	\section{\scenarioFellowship}
		The first thing that John wants to do, after editing his profile, is to search for Jill. So he types Jill's full name in the search bar and opens her profile. Jill is using \SocialBattle{} for weeks, so his character is already at level 16 (John's one is level 1) and has a lot of abilities and items equipped which John doesn't know about. John decides to click on ``Follow'', in this way he could follow all Jill's progresses, such as levelling up, new mobs killed, new items collected and so on.

	\section{\scenarioRooms}
		Some weeks have passed, John is now a veteran. As any other day, John logs in to \SocialBattle{} and enters ``The Shop'' room. This room provides the possibility to buy items from an AI controlled merchant. John is out of ``potions'' and so he opens a chat with the merchant and types ``\\buy potion''. Doing this, John looses 125 guils, but gains a potion in his inventory.\\
		Now John can go to skill his character and so he enters his favorite room: the ``Thunder Plains''. In this room he can find his favorite mobs: ``Iron Giant'' and ``Qactuar''. In fact, after a few seconds, a wild ``Qactuar'' spawns on the bottom of his screen and the battle starts.

	\section{\scenarioBattle}
		The ``Qactuar'' always performs his strong attack ``1000 Needles'' which inflicts 1000 points of damage. John knows that he has to kill it rapidly so he starts repeatedly attacking it.\\
		As just as John types ``\\'' a drop down menu appears downside the input bar containing all the possible abilities that his character can perform. John proceeds in typing ``att'' and the drop down menu reduces to suggest ``attack''. John presses ``Enter'' and the physical attack is selected. The ATB bar charges and, once it has arrived to full charge, the attack is performed and ``Qactuar'' looses 242 points of damage.\\
		After a few attacks the mob dies and John gains a ``Speed Sphere'' (item) that is added to John's inventory, 350 EXP and 48 guils.

		After killing the ``Qactuar'' John looks at the ``Thunder Plains'' page. In the center of the page he can find the loots discarded by other users at the end of a fight. Clicking on ``grab'' John takes other two potions.

		After this fight John is told by Jill that \textit{Whatsapp} is giving the possibility in its official site to \SocialBattle{}'s user to fight a custom mob. John goes to \textit{Whatsapp} site and on the top right corner there is a widget. John clicks on it and, after logging in, the battle against ``Billions'' mob starts.
	